---
title: "Categorical Correlation Matrix"
format: 
  revealjs:
    theme: moon 
editor: visual
---

## intro slide on what it does

## why would you need it?

-   corrplot only works for continuous variables as it uses Pearson's R to generation correlation coefficients
-   But what if we want to assess the correlation between categorical variables?

## What does this package do?

-   uses cramersV to calculate correlation coefficient between categorical variables
-   generates a table with correlation values
-   generates correlation matrix plot

## Example Data

-   show birds dataset

```{r, echo = F}
birds <- read.csv("corrcat/data/birds.csv")
print(birds[1:10,])
```

## Example code

```{r, echo = T}

# library(corrcat)
# 
# # calculates cramversV scores for all categorical variables 
# calculate_cramers_v(birds)
# 
# # produces a correlation matrix with using the cramersV scores 
# corrplot_cat(birds)
# 
# # prints both the cramers scores in a table and the correlation matrix 
# cramermatrix_cat(birds[1:4])

```

## notes of the package

-   only works for comparing nominal categorical variables
-   will need to filter data set of continuous variables prior to using function

```{r, echo = T}
# cramermatrix_cat(birds[1:4])
```
